A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-16 MSRChallenge2016.tex
Fixed the bibliography references

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{clegoues@cs.cmu.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}
\todo{High level todo, probably for Mau since I think it's his bibtex: please
  change the bibtex keys to take the form ``lastnameYear'', and then fix the
  citations.}
\todo{Please move the bibitems included explicitly in this document into sigproc.bib
   and use bibtex.}
\todo{Also, please always include a non-breaking space (a tilde, look at the
  latex for an example) between a word and the cite tag, and include multiple
  references on a line in a single citation tag (again, look at the latex for an
  example; I'll do this once, but would like you to fix the rest when appropriate.}
Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically \cite{dongsun,weimer,claire,kai}, one of the
most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.

@@

Another well known approach is PAR \cite{dongsun}, which creates 10 different
repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 7 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by \cite{robert}.

@@

\section{Methodology}
Our methodology is applied to the latest official data dump of Github as of
September 2015 provided by \cite{robert}. In the following subsections, we first
describe data source and objective of our study. We then describe how we detect
bug fixing patterns in PAR to find out how common they are the dataset. Last but
not least, we describe our approach to detect Delete, Replace, and Append
bug-fixing patterns.

@@

\subsection{Data Source and Research Objective}
We used the Boa platform \cite{robert} to be able to query the Github repository
looking for patterns that humans use to patch errors in the their code. Our main
goal is to provide guidelines for automatic error fixing approaches by providing
necessary information regarding historical replace, delete and append statements
in human written patches.

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et
al. paper~\cite{dongsun}. The following is the description of each considered
pattern. 
\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
  but we need to explain why.}
  \begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
\end{enumerate}

To analyze bug fixing patterns, we utilizes Boa's language
infrastructure~\cite{robert}. It contains a large number of dataset and provide
a domain specific language to perform analysis on source code. Despite this
advantage, Boa still have limited capability that prevents us from performing
precise detection of bug fixing patterns. For example, it is unable to perform a
diff between two file versions, which is needed to compare the pre-fix and the
post-fix version of a buggy file. Thus, rather than finding the exact count of
bug fixing patterns, we will find an approximate count of those patterns. The
following are descriptions on how we detect each pattern.

@@

\subsection{Replace Query}
The replace query is a query in which first we set the project that we are going
to use, which is the Github dump of September 2015 provided by \cite{robert}.

@@

\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM, COM, CBC, IAO, ANC, and AOB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, and 0.28\% of buggy files. We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB. If we assume that these patterns never appear together in the dataset, these patterns cover 14.21\% of buggy files. Kim et al. mentioned that the patterns that they use cover almost 30\% of real patches~\cite{dongsun}. Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together. Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound. This suggests that common bug fixing patterns might not be as common as it appeared to be.

@@

\subsubsection{Likeliness of replacement}
This study is directly applicable to automatic software repair. Most common
tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire}
first find a faulty statement using several different fault localization
techniques \cite{zach}, and once they have that faulty statement, they apply
different kinds of edits to it, usually at random. Which makes it equally likely
to replace an statement for another without looking at the kinds of statements
being replaced.

@@

\section{Related Work}
A similar study was performed by Dongsun Kim et al. \cite{dongsun} in which they
look for the most common ways in which programmers patch bugs in software. The
researchers developed a variation of the tool Genprog \cite{weimer}\cite{claire}
with several different templates resembling patters programmers use to patch
bugs.

A good complement for this paper is \cite{hao}, where they search additions and
deletions in a smaller data set. In this paper, we focus on the replacements,
which have been left out of the analysis of \cite{hao}.

@@

\begin{thebibliography}{9}

\bibitem{robert}
  Robert Dyer et al.,
  \emph{Boa: A Language and Infrastructure for Analyzing Ultra-Large-Scale Software Repositories},
35th International Conference on Software Engineering; ICSE 2013, San Francisco CA, USA

\bibitem{hao}
Hao Zhong, Zhendong Su
\emph{An Empirical Study on Real Bug Fixes},
In Proceedings of ICSE 2015, Firenze, Italy, May 16-24, 2015.

\bibitem{kai}
Kai Pan et al.
\emph{Towards an understanding of bug fix patterns},
Journal
Empirical Software Engineering
Volume 14 Issue 3, June 2009 
Pages 286 - 315

\bibitem{dongsun}
Dongsun Kim et al.
\emph{Automatic patch generation learned from human-written patches},
Proceeding
ICSE '13 Proceedings of the 2013 International Conference on Software Engineering

\bibitem{zach}
Zachary P.Fry and Westley Weimer
\emph{A human study of fault localization accuracy},
ICSM '10 Proceedings of the 2010 IEEE International Conference on Software Maintenance

\bibitem{claire}
Claire Le Goues, ThanhVu Nguyen, Stephanie Forrest, Westley Weimer
\emph{GenProg: A Generic Method for Automated Software Repair.} 
IEEE Trans. Software Engineering 38(1): 54-72 (January/February 2012)

\bibitem{weimer}
Westley Weimer, ThanVu Nguyen, Claire Le Goues, Stephanie Forrest
\emph{Automatically Finding Patches Using Genetic Programming.}
International Conference on Software Engineering (ICSE) 2009: 364-374

\end{thebibliography}

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{author@edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\section{Introduction}

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}, one of the
most accepted approaches so far has been GenProg~\cite{weimer2009,legoues2012}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.

@@

Another well known approach is PAR~\cite{kim2013}, which creates 10 different
repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 7 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

@@

\section{Methodology}
Our methodology is applied to the latest official data dump of Github as of
September 2015 provided by~\cite{dyer2013}. In the following subsections, we first
describe data source and objective of our study. We then describe how we detect
bug fixing patterns in PAR to find out how common they are the dataset. Last but
not least, we describe our approach to detect Delete, Replace, and Append
bug-fixing patterns.

@@

\subsection{Data Source and Research Objective}
We used the Boa platform~\cite{dyer2013} to be able to query the Github repository
looking for patterns that humans use to patch errors in the their code. Our main
goal is to provide guidelines for automatic error fixing approaches by providing
necessary information regarding historical replace, delete and append statements
in human written patches.

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et
al. paper~\cite{kim2013}. The following is the description of each considered
pattern. 
\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
  but we need to explain why.}
  \begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
\end{enumerate}

To analyze bug fixing patterns, we utilizes Boa's language
infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
a domain specific language to perform analysis on source code. Despite this
advantage, Boa still have limited capability that prevents us from performing
precise detection of bug fixing patterns. For example, it is unable to perform a
diff between two file versions, which is needed to compare the pre-fix and the
post-fix version of a buggy file. Thus, rather than finding the exact count of
bug fixing patterns, we will find an approximate count of those patterns. The
following are descriptions on how we detect each pattern.

@@

\subsection{Replace Query}
The replace query is a query in which first we set the project that we are going
to use, which is the Github dump of September 2015 provided by~\cite{dyer2013}.

@@

\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM, COM, CBC, IAO, ANC, and AOB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, and 0.28\% of buggy files. We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB. If we assume that these patterns never appear together in the dataset, these patterns cover 14.21\% of buggy files. Kim et al. mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}. Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together. Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound. This suggests that common bug fixing patterns might not be as common as it appeared to be.

@@

\subsubsection{Likeliness of replacement}
This study is directly applicable to automatic software repair. Most common
tools for automatic software repair~\cite{kim2013,weimer2009,legoues2012}
first find a faulty statement using several different fault localization
techniques~\cite{fry2010}, and once they have that faulty statement, they apply
different kinds of edits to it, usually at random. Which makes it equally likely
to replace an statement for another without looking at the kinds of statements
being replaced.

@@

\section{Related Work}
A similar study was performed by Dongsun Kim et al.~\cite{kim2013} in which they
look for the most common ways in which programmers patch bugs in software. The
researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
with several different templates resembling patters programmers use to patch
bugs.

A good complement for this paper is~\cite{zhong2015}, where they search additions and
deletions in a smaller data set. In this paper, we focus on the replacements,
which have been left out of the analysis of~\cite{zhong2015}.

@@
